---
output:
  github_document
---

ochathemes
============

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  eval = FALSE,
  fig.width = 10,
  fig.path = "inst/img/",
  comment = "#> ")

hook_output <- knitr::knit_hooks$get("output")
knitr::knit_hooks$set(output = function(x, options) {
   lines <- options$output.lines
   if (is.null(lines)) {
     return(hook_output(x, options))  # pass to default hook
   }
   x <- unlist(strsplit(x, "\n"))
   more <- "..."
   if (length(lines)==1) {        # first n lines
     if (length(x) > lines) {
       # truncate the output, but add ....
       x <- c(head(x, lines), more)
     }
   } else {
     x <- c(if (abs(lines[1])>1) more else NULL,
            x[lines],
            if (length(x)>lines[abs(length(lines))]) more else NULL
           )
   }
   # paste these lines together
   x <- paste(c(x, ""), collapse = "\n")
   hook_output(x, options)
 })

knitr::opts_chunk$set(
  comment = "#>",
  echo = TRUE,
  collapse = TRUE,
  eval = FALSE,
  warning = FALSE,
  message = FALSE
)
```

[![GitLab CI Build Status](https://gitlab.com/dickoa/ochathemes/badges/master/build.svg)](https://gitlab.com/dickoa/ochathemes/pipelines) 
[![Codecov Code Coverage](https://codecov.io/gl/dickoa/ochathemes/branch/master/graph/badge.svg)](https://codecov.io/gl/dickoa/ochathemes)
[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)

`ochathemes` is package providing `ggplot2` themes and theme components inspired by OCHA graphics stylebook.

## Installation

This package is not on yet on CRAN and to install it, you will need the [`remotes`](https://github.com/r-lib/remotes) package.

```{r}
## install.packages("remotes") 
remotes::install_gitlab("dickoa/ochathemes")
```

```{r}
library("ochathemes")
```

## Meta

* Please [report any issues or bugs](https://gitlab.dickoa/ochathemes/issues).
* License: MIT
* Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
